\documentclass[a4paper,12pt]{article}
\pagenumbering{gobble}
\usepackage{sectsty}
\usepackage{enumitem}
\usepackage[tmargin=1in,bmargin=0.5in]{geometry}
\usepackage[utf8x]{inputenc}
\usepackage[pdftex,unicode=true]{hyperref}
\usepackage{graphicx}
\usepackage{tikz}

\begin{document}

\section*{Mark Karpov}

Tel.: (+33) 0661355676\\
Email: markkarpov92@gmail.com\\
GitHub: \href{https://github.com/mrkkrp}{https://github.com/mrkkrp}\\
Twitter: \href{https://twitter.com/mrkkrp}{https://twitter.com/mrkkrp}\\
LinkedIn: \href{https://www.linkedin.com/in/mark-karpov-73789914a}{https://www.linkedin.com/in/mark-karpov-73789914a}\\
StackOverflow: \href{https://stackoverflow.com/users/3687048/mark}{https://stackoverflow.com/users/3687048/mark}\\
The resume is also available online: \href{https://markkarpov.com/resume.html}{https://markkarpov.com/resume.html}

\sectionfont{\fontsize{12}{15}\selectfont\sectionrule{0pt}{0pt}{-5pt}{0.8pt}}

\section*{Summary}

I'm a software engineer specializing in functional programming using strong
static type systems. I have worked many years as a full-time consultant
helping our clients design and build correct, robust, and maintainable
software. Being a consultant allowed me to participate in more projects that
a typical software engineer gets to work on. I've developed the ability for
critical thinking, making wise trade-offs, analyzing and exploiting
advantages of various technologies to satisfy needs of business. I also
learned how to handle different personalities and collaborate with diverse
teams. My personal projects include high-profile Haskell libraries,
tutorials, and a technical blog.

\section*{Professional experience}

\begin{itemize}[noitemsep]
\item \textbf{January 14, 2019--present.} Senior software engineer at
  \href{https://tweag.io}{Tweag}, Paris, France. Working as a consultant
  most part of the time, but also building OSS, writing blog posts, doing
  interviews for new hires, etc.
\item \textbf{January 25, 2018--January 11, 2019.} Software engineer at
  \href{https://tweag.io}{Tweag} (remote). Worked as a consultant with a
  number of clients, helped developing Bazel rules for Haskell.
\item \textbf{May 4, 2016--May 20, 2017.} Tier 2 Haskell developer at
  \href{https://www.stackbuilders.com/}{Stack Builders} (remote). Consulting
  several clients mostly from the US. Agile. Another part of the job was
  writing tutorials and blog posts to increase visibility of the company.
\end{itemize}

\section*{Open source}

\begin{itemize}[noitemsep]
\item \href{https://github.com/mrkkrp/megaparsec}
  {Megaparsec---Industrial-strength monadic parser combinator library.
    \newline
    https://github.com/mrkkrp/megaparsec}
\item \href{https://github.com/tweag/ormolu}
  {Ormolu---A formatter for Haskell source code.
    \newline
    https://github.com/mmark-md/mmark}
\item \href{https://github.com/mrkkrp/req}
  {Req---Easy-to-use, type-safe, expandable, high-level HTTP library.
    \newline
    https://github.com/mrkkrp/req}
\item \href{https://github.com/mrkkrp/zip}
  {Zip---Efficient library for manipulating zip archives.
    \newline
    https://github.com/mrkkrp/zip}
\end{itemize}

The full list can be found at \href{https://markkarpov.com/oss.html}{https://markkarpov.com/oss.html}.

\pagebreak

\section*{Writing}

\begin{itemize}[noitemsep]
\item I've authored a number of tutorials as part of my job and on my own,
  see \href{https://markkarpov.com/learn-haskell.html}{https://markkarpov.com/learn-haskell.html}.
\item Blog posts are available at
  \href{https://markkarpov.com/posts.html}{https://markkarpov.com/posts.html},
  see e.g.
  \href{https://www.tweag.io/posts/2019-09-06-why-haskell-is-important.html}{“Why
    Haskell is important”}.
\end{itemize}

\section*{Technologies}

\begin{itemize}[noitemsep]
\item Nix is one of the main technologies we use at Tweag. I run NixOS as my
  primary OS and use Nix daily in my work and for personal projects.
\item Strong knowledge of Git.
\item CI: Travis CI, Circle CI, Buildkite.
\item Databases: PostgreSQL, MySQL.
\item AWS.
\item Linux server.
\item Docker.
\item Bash/Python/Haskell scripting.
\item Dependent types, theorem provers: Coq.
\item Build systems: make, shake, Bazel.
\item Server automation: Ansible.
\item Front-end: HTML (5), CSS (Bootstrap), JavaScript (jQuery, AJAX,
  websockets).
\item Other languages I know: C, C++, Python, Common Lisp, Emacs Lisp.
\end{itemize}

\section*{Soft skills}

\begin{itemize}[noitemsep]
\item I know how to work with people who have different types of
  personalities and skill levels.
\item Flexible and open to criticism. If I'm presented with good arguments,
  I can change my opinion. It's not hard for me to admit that I may be
  wrong.
\item Active in discussion, good communicator.
\item I speak Russian (native), English (fluent), and French (fluent).
\end{itemize}

\section*{Education}

\begin{itemize}[noitemsep]
\item 2009--2014---Polzunov Altai State Technical University. Engineer
  degree in informational technology and measuring engineering.
\end{itemize}

\begin{flushright}
  \today
\end{flushright}

\end{document}
